Flexible Scientific Data Management for Plant Phenomics Research

### 2013-03-11 s4biodiv2013/PODD-S4BIODIV-Submission.tex
fix sentence to be meaningful
keywords added in again

%\keywords{eResearch, Semantic Web, RDF, OWL, Data collection citation, BagIt,
% Data Access Portal}

@@

CSIRO ASC shared facilities \cite{ASC} are used to process the raw
PlantScan\textsuperscript{\texttrademark} data to derive data products (meshes).
Raw data and meshes are collected using the BagIt format \cite{Kunze2011} and
stored in the ASC archival system. ASC High Performance Compute (HPC) hosts
(systems with high processor count and large memory) are taken advantage of to
create and verify bags more rapidly than would be possible on conventional
computer systems. The DAP to store collections of
PlantScan\textsuperscript{\texttrademark} 
raw images and processed mesh data as bags. Currently, one bag is equivalent to
a single batch scanned on the
PlantScan\textsuperscript{\texttrademark}
local software system, which usually means the same kind of plant with different
genotypes scanned under one  experiment configuration profile.

>>>>

\keywords{eResearch, Semantic Web, RDF, OWL, Data collection citation, BagIt, Data Access Portal}

@@

CSIRO ASC shared facilities \cite{ASC} are used to process the raw
PlantScan\textsuperscript{\texttrademark} data to derive data products (meshes).
Raw data and meshes are collected using the BagIt format \cite{Kunze2011} and
stored in the ASC archival system. ASC High Performance Compute (HPC) hosts
(systems with high processor count and large memory) are taken advantage of to
create and verify bags more rapidly than would be possible on conventional
computer systems. DAP is used to store collections of
PlantScan\textsuperscript{\texttrademark} 
raw images and processed mesh data as bags. Currently, one bag is equivalent to
a single batch scanned on the
PlantScan\textsuperscript{\texttrademark}
local software system, which usually means the same kind of plant with different
genotypes scanned under one  experiment configuration profile.
